\NAME: A framework for \\ Efficient Intrusion Detection\\ in the Internet of Things

### 2014-10-23 paper.tex
changed formatting of subsection titles
marked conclusion and future work as TODO
minor changes while reviewing before starting ;-)

\subsection{Detecting Intrusions}
\label{detection}

@@

\subsection{Cooperative Decision Making}
\label{coorperative}

@@

\subsection{Software Attestation}
\label{subsection:attestation}

@@

Figure \ref{fig:classification} gives a visual overview of the classification
presented above.

@@

\begin{figure}[!ht]
\captionof{lstlisting}{ID Algorithm Pattern\label{alg:id-algo-pattern}}
\begin{algorithmic}[1]
  \Require{nodes, global storage for information about nodes}
  \Function{process\_message}{$msg$}
    \ForEach{$byte \in msg$} \label{alg:id-algo-pattern-loop1}
     \State \dots \Comment{analyze byte-sequences}
    \EndFor
    \Let{$nodes_x$}{value}  \Comment{optionally update node info}
    \State \Call{send}{$nodes_y$, ``info''} \Comment{optionally exchange info} \label{alg:id-algo-pattern-send1}
  \EndFunction
  \State
  \Function{do\_housekeeping}{}
    \ForEach{$node \in nodes$} \label{alg:id-algo-pattern-loop2} \label{alg:id-algo-pattern-common-data}
      \If{$node > \dots$} \Comment{validate recorded value}
        \State \dots \Comment{take actions}
        \State \Call{send}{$node$, ``info''} \Comment{e.g. communicate} \label{alg:id-algo-pattern-send2}
      \EndIf
    \EndFor
  \EndFunction
  \State
\end{algorithmic}
\end{figure}

@@

\subsection{Loops and Common Data}

@@

\subsection{Network Usage and Heterogeneity}

@@

\subsection{The Meaning of Loops}

@@

\subsection{A DSL for Nodes}

@@

\subsection{Unified Messaging}

@@

\subsection{Code Generator}

@@

\subsection{Semantic Model}

@@

\subsection{Functional Code Fusion}

@@

\subsection{Code Model}

@@

\subsection{Software Library}

@@

\subsection{Architecture}

@@

This hierarchy is important from a development effort point of view. The level
of dependency on the platform also dictates the level of effort to implement
changes to the platform. For example: changing the language will require a
complete rewrite of the software library and a partial rewrite of the language
description of the generator. Although this is a one-time effort, it is
important in relation to the scalability of the framework.

\subsection{Implementation}

@@

\subsection{Experimental Results}

>>>>

\subsection*{Detecting Intrusions}
\label{detection}

@@

\subsection*{Cooperative Decision Making}
\label{coorperative}

@@

\subsection*{Software Attestation}
\label{subsection:attestation}

@@

Figure \ref{fig:classification} visually summarizes the dual classification
presented above.

@@

\begin{figure}[b]
\captionof{lstlisting}{ID Algorithm Pattern\label{alg:id-algo-pattern}}
\begin{algorithmic}[1]
  \Require{nodes, global storage for information about nodes}
  \Function{process\_message}{$msg$}
    \ForEach{$byte \in msg$} \label{alg:id-algo-pattern-loop1}
     \State \dots \Comment{analyze byte-sequences}
    \EndFor
    \Let{$nodes_x$}{value}  \Comment{optionally update node info}
    \State \Call{send}{$nodes_y$, ``info''} \Comment{optionally exchange info} \label{alg:id-algo-pattern-send1}
  \EndFunction
  \State
  \Function{do\_housekeeping}{}
    \ForEach{$node \in nodes$} \label{alg:id-algo-pattern-loop2} \label{alg:id-algo-pattern-common-data}
      \If{$node > \dots$} \Comment{validate recorded value}
        \State \dots \Comment{take actions}
        \State \Call{send}{$node$, ``info''} \Comment{e.g. communicate} \label{alg:id-algo-pattern-send2}
      \EndIf
    \EndFor
  \EndFunction
  \State
\end{algorithmic}
\end{figure}

@@

\subsection*{Loops and Common Data}

@@

\subsection*{Network Usage and Heterogeneity}

@@

\subsection*{The Meaning of Loops}

@@

\subsection*{A DSL for Nodes}

@@

\subsection*{Unified Messaging}

@@

\subsection*{Code Generator}

@@

\subsection*{Semantic Model}

@@

\subsection*{Functional Code Fusion}

@@

\subsection*{Code Model}

@@

\subsection*{Software Library}

@@

\subsection*{Architecture}

@@

This hierarchy is important from a development effort point of view. The level
of dependency on the targeted platform also dictates the level of effort to
implement changes to that platform. For example: to emit a different language
will require a complete rewrite of the software library and a partial rewrite
of the language description of the generator. Although this is a reusable,
one-time effort, it is important in relation to the scalability of the
framework.

\subsection*{Implementation}

@@

\subsection*{Experimental Results}
